### 2017-08-18 README.Rmd
mostly adds reqs to travis+appveyor

        @article{hejazi2017methyvim,
          doi = {},
          url = {},
          year  = {2017},
          month = {},
          publisher={Faculty of 1000 Ltd},
          volume = {},
          author = {Hejazi, Nima S and Hubbard, Alan E and {van der Laan}, Mark
            J},
          title = {methyvim: Differential methylation analysis with targeted
            esitmates of nonparametric variable importance measures},
          journal = {F1000Research}
        }

>>>>

        @article{hejazi2017methyvim,
          doi = {},
          url = {},
          year  = {2017},
          month = {},
          publisher = {},
          volume = {},
          author = {Hejazi, Nima S and Hubbard, Alan E and {van der Laan}, Mark
            J},
          title = {methyvim: Nonparametric differential methylation analysis
            with targeted estimates of variable importance measures},
          journal = {}
        }
